\section{Installation}

\subsection{System Requirements}

Running SyncDET requires one or more UNIX, Linux, or cygwin systems. 
The controller has only been tested for OSX and requires the
following:
\begin{enumerate}
\item Python 2.7+ installed
\item {\tt git}, {\tt tar}, and {\tt grep}.
\end{enumerate}
The requirements for each actor follow:
\begin{enumerate}
\item Python 2.6+ installed.
\item An {\tt ssh} daemon server installed and running; future support can be made for
{\tt telnet} or {\tt rlogin} if desired. The controller should be able to login
without entering a password.
\item Commands {\tt ps}, {\tt grep}, {\tt tar}, and {\tt sed} installed. {\tt ps} must
support the option {\tt -eo pid,cmd}, which lists all processes with a PID and a
command line per row.
\end{enumerate}

\subsection{Acquiring Source Code}
\begin{verbatim}
$ mkdir ~/repos; cd ~/repos
$ git clone ssh://z.arrowfs.org/repos/aerofs.syncdet
\end{verbatim}

\subsection{Actor VMs}
SyncDET-ready virtual machines have been created for Linux, OSX Leopard, Windows
7 and Windows XP. They are shared as bzipped tarballs in an AeroFS library
somewhere (ask Mark or Weihan). They satisfy the system requirements listed
above, except for passwordless ssh; {\bf you must copy over your public key}. To
extract the linux VM, for example:
\begin{verbatim}
$ tar -xvf syncdet-ubuntu1110_32.tar.bz2 -C <parent directory of VM>
\end{verbatim}

\subsection{Systems Configuration}
You must manually configure the actor and controller systems. 

\paragraph{Actors} 
List the hostname or IP address of all systems to be used as actors in \\*
{\tt [SyncDETRepo]/syncdet/actor\_def.py}. Specifically modify the d\_actors
dictionary:
\begin{verbatim}
# the dictionary definition of the actors
d_actors = [
            { 'address': '192.168.1.16' },
            { 'address': '192.168.1.17' },
            ]
\end{verbatim}

\paragraph{Controller} 
You need to specify the hostname of the localhost from which you will launch
SyncDET scenarios (the localhost will be the controller). This is necessary
because actors connect back to the controller for certain tasks. It can be
specified by modifying {\tt [SyncDETRepo]/syncdet/config.py}:
\begin{verbatim}
# the address or the host name of the controller
CONTROLLER_ADDR = "192.168.1.15"
\end{verbatim}

\subsection{Running the Demo Scenario}
\begin{verbatim}
$ cd [SyncDETRepo]/syncdet
$ ./det.py -f default.scn
\end{verbatim}

or simply

\begin{verbatim}
$ ./det.py
\end{verbatim}
